\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}
\usepackage{parskip}

\definecolor{primary}{HTML}{4338CA}
\definecolor{darktext}{HTML}{1E293B}
\definecolor{graytext}{HTML}{64748B}

\hypersetup{colorlinks=true, linkcolor=primary, urlcolor=primary}
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{darktext}}{}{0em}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\color{graytext}CardioRisk AI — Project Report}
\fancyfoot[C]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\begin{document}

% ── Title ─────────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE\bfseries\color{primary} CardioRisk AI}\\[4pt]
    {\large Cardiovascular Risk Prediction Using Machine Learning}\\[12pt]
    \textbf{GenAI Capstone Project Report}\\[16pt]
    \begin{tabular}{ll}
        \textbf{Team Lead:} & Lakshya \\
        \textbf{Members:}   & Abhishek Rana, Abhinav Choudhary, Varun Sharma \\
    \end{tabular}\\[8pt]
    {\color{graytext} March 2026 \quad$\cdot$\quad \url{https://huggingface.co/spaces/lakshyalamba/cardiorisk-ai}}
\end{center}

\vspace{6pt}

% ── Introduction ──────────────────────────────────────────────────────────────
\section{Introduction}
Cardiovascular diseases are the leading cause of death globally. Early risk detection can significantly reduce mortality through timely intervention. \textbf{CardioRisk AI} is a machine learning system that predicts cardiovascular risk from patient health data and presents results through an interactive Streamlit dashboard deployed on HuggingFace Spaces.

% ── Dataset ───────────────────────────────────────────────────────────────────
\section{Dataset \& Preprocessing}
The synthetic health dataset contains \textbf{10,000 records} with 11 columns (10 features + 1 target). After dropping 500 rows with missing target values, \textbf{9,500 records} were used.

\begin{table}[H]
\centering\small
\begin{tabular}{ll}
\toprule
\textbf{Numerical (5)} & age, systolic\_bp, cholesterol, max\_heart\_rate, bmi \\
\textbf{Categorical (5)} & sex, chest\_pain, smoker, diabetes, exercise\_angina \\
\textbf{Target} & risk (0 = Low, 1 = High) \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Preprocessing steps:} (1)~Missing values filled with median (numerical) and mode (categorical), (2)~One-hot encoding for categorical features, (3)~StandardScaler on numerical features, (4)~80/20 stratified train-test split $\rightarrow$ 7,600 train / 1,900 test samples.

\textbf{Class distribution:} 7,165 high-risk (75.4\%) and 2,335 low-risk (24.6\%).

% ── Model ─────────────────────────────────────────────────────────────────────
\section{Model Training \& Results}
We used \textbf{Logistic Regression} (\texttt{max\_iter=1000}) for binary classification. It is interpretable, efficient, and outputs calibrated probabilities suitable for risk scoring.

\subsection{Performance Metrics}
\begin{table}[H]
\centering\small
\begin{tabular}{lr|lr}
\toprule
\textbf{Metric} & \textbf{Value} & \textbf{Metric} & \textbf{Value} \\
\midrule
Accuracy  & 91.16\% & AUC-ROC & 96.68\% \\
Precision (weighted) & 91\% & Recall (weighted) & 91\% \\
F1 Score (weighted)  & 91\% & & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Confusion Matrix (1,900 test samples)}
\begin{table}[H]
\centering\small
\begin{tabular}{l|cc}
 & \textbf{Pred: No Risk} & \textbf{Pred: At Risk} \\
\midrule
\textbf{Actual: No Risk} & TN = 361 & FP = 106 \\
\textbf{Actual: At Risk} & FN = 62  & TP = 1,371 \\
\end{tabular}
\end{table}

\subsection{Top Feature Coefficients}
\begin{table}[H]
\centering\small
\begin{tabular}{lr|lr}
\toprule
\textbf{Feature} & \textbf{Coeff.} & \textbf{Feature} & \textbf{Coeff.} \\
\midrule
Smoker (Yes)   & +4.439 & Cholesterol    & +1.728 \\
Diabetes (Yes) & +4.388 & Systolic BP    & +1.834 \\
Age            & +1.950 & Max Heart Rate & $-$0.002 \\
\bottomrule
\end{tabular}
\end{table}

Smoking and diabetes are the strongest predictors, with coefficients over 4$\times$ larger than any other feature.

% ── Dashboard ─────────────────────────────────────────────────────────────────
\section{Dashboard}
Built with \textbf{Streamlit} and \textbf{Plotly}, deployed on \textbf{HuggingFace Spaces}:

\begin{itemize}[noitemsep, topsep=4pt]
    \item \textbf{KPI Dashboard:} Model metric cards, dataset stats, class distribution charts
    \item \textbf{Visual Analysis:} ROC Curve (AUC = 0.97), Confusion Matrix heatmap, Feature Weights bar chart
    \item \textbf{Prediction System:} Patient input form $\rightarrow$ real-time risk score gauge + risk indicators
\end{itemize}

% ── Tech Stack ────────────────────────────────────────────────────────────────
\section{Technology Stack}
\begin{table}[H]
\centering\small
\begin{tabular}{ll|ll}
\toprule
scikit-learn & ML model \& metrics & Streamlit & Dashboard UI \\
pandas / NumPy & Data processing & Plotly & Interactive charts \\
matplotlib / seaborn & Notebook plots & HuggingFace & Deployment \\
\bottomrule
\end{tabular}
\end{table}

% ── Conclusion ────────────────────────────────────────────────────────────────
\section{Conclusion}
CardioRisk AI achieves \textbf{91.16\% accuracy} and \textbf{0.97 AUC-ROC}, identifying smoking and diabetes as the top cardiovascular risk factors. The interactive dashboard enables real-time patient risk assessment and is publicly accessible via HuggingFace Spaces.

\textbf{Future scope:} Real-world clinical datasets, ensemble models (XGBoost, Random Forest), patient history tracking, and EHR system integration.

\end{document}
